### 2017-10-13 Gruba/02-overview.tex

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
Note that $M_b.O$ is a user, and $B_u$ is a set of $M_b$.

@@

\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

>>>>

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
Note that $M_b.O$ is a user $u$, and $B_u$ is a set of $M_b$.

@@

\stitle{Sina Microblog Data.} It is the data crawled to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.
